Deep Learning

### 2015-01-11 deepreview.tex
added a reference on the importance of the gating of the self-loop gate for LSTMs

Recent work~\citep{Chung-et-al-NIPSDL2014} suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence of
of the gate controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.

>>>>

Recent work~\citep{Chung-et-al-NIPSDL2014,Yao-et-al-SLU-workshop2014} 
suggests that not all the elements of the LSTM
architecture are required, the crucial element being the presence of
of the gate controlling the leaking rate (or time constant) of the cell.
%It is not yet clear which aspects of the complicated architecture of LSTMs
%are really necessary. Memory cells are a good way of allowing the
%backpropagated error derivatives to neither explode nor vanish, but they
%are not the only way.  For example, recurrent nets with rectified linear
%hidden units that use the non-linear function $y=max(0,x)$ are much simpler
%than LSTMs and if the recurrent weight matrix is initialized to be close to
%the identity matrix they work about as well as LSTMs both for toy problems
%involving very long-range temporal structure and for real tasks like
%predicting the next word in text\citep{LeHinton}.
